---
title: "code_Xinyan"
author: "Xinyan Zheng"
date: "December 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(leaps)

#load the data
hos = read.csv("./data/cleaned_data_for_analyses.csv") %>% 
  select(-X, -postalcode,-facilityname,-facilityzip, -patientid, -visitid, -date) %>% 
  mutate(is30dayreadmit = as.factor(is30dayreadmit), icu_flag = as.factor(icu_flag))

hos_no_outlier = read.csv("./data/data_no_outliers.csv") %>% 
  select(-X, -postalcode,-facilityname,-facilityzip, -patientid, -visitid, -date) %>% 
  mutate(is30dayreadmit = as.factor(is30dayreadmit), icu_flag = as.factor(icu_flag))

hos_outlier = read.csv("./data/outlier_patients.csv")%>%
  select(-X, -postalcode,-facilityname,-facilityzip, -patientid, -visitid, -date) %>% 
  mutate(is30dayreadmit = as.factor(is30dayreadmit), icu_flag = as.factor(icu_flag))

```


```{r}

# using criterion-based method

attach(hos)
model_bw <- lm(log_length_of_stay ~ is30dayreadmit + evisit + age 
               + gender + maritalstatus + insurancetype + heartrate_transformed
               + respirationrate_transformed+mean_arterial_pressure)
model_fw_new <- lm(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + temperature_cat  + maritalstatus 
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure)
model_sw_0.05 <- lm(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + temperature_cat + 
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure)
model_sw_0.10 <- lm(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + gender + maritalstatus + temperature_cat 
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure)
AIC(model_bw, model_fw_new, model_sw_0.05, model_sw_0.10)



##########this is the main function#######

criterion_bw <- regsubsets(log_length_of_stay ~ is30dayreadmit + evisit + age 
               + gender + maritalstatus + insurancetype + heartrate_transformed
               + respirationrate_transformed+mean_arterial_pressure, data = hos,
               nvmax= 15, nbest = 1)
criterion_fw <- regsubsets(log_length_of_stay ~ is30dayreadmit + evisit + age 
               + heartrate_transformed + respirationrate_transformed 
               + mean_arterial_pressure + insurancetype + race, data = hos, nvmax= 15
               , nbest = 1)
criterion_fw_new <- regsubsets(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + temperature_cat  + maritalstatus 
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure, data = hos, nvmax= 15, nbest = 1)
criterion_sw_0.05 <- regsubsets(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + temperature_cat + 
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure, data = hos, nvmax= 15, nbest = 1)
criterion_sw_0.10 <- regsubsets(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + gender + maritalstatus + temperature_cat 
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure, data = hos, nvmax= 15, nbest = 1)

#make plots to show the value of criterion

criterion_plot <- function(criterion, data, method){
  
  res_cri <- summary(criterion)
  par(mfrow=c(2,2))
  plot(1:dim(res_cri$which)[1], res_cri$cp, pch=16, xlab="No of parameters", ylab="Cp Statistic")
  abline(0,1)
  plot(1:dim(res_cri$which)[1], res_cri$adjr2, pch=16, xlab="No of parameters", ylab="Adj R2")
  plot(1:dim(res_cri$which)[1], res_cri$rss, pch=16, xlab="No of parameters", ylab="rss")
  plot(1:dim(res_cri$which)[1], res_cri$bic, pch=16, xlab="No of parameters", ylab="BIC")
}

criterion_plot(criterion_bw, data= hos, method = "backward eliminaton") 
criterion_plot(criterion_fw, data= hos, method = "forward eliminaton" )
criterion_plot(criterion_sw_0.10, data= hos, method = "stepwise 0.10" ) 
criterion_plot(criterion_sw_0.05, data= hos, method = "stepwise 0.05")
criterion_plot(criterion_fw_new, data= hos, method = "forward elimination by hand")
 
# make table to show the value of criterion

best <- function(criterion) {
  
  subsets <- with(summary(criterion), cbind(p = as.numeric(rownames(which)),
                                            which, rss, rsq, adjr2, cp, bic))
  return(round(subsets,4))%>% as.tibble()
}  

best(criterion_bw)%>% 
  select(p, rss, rsq, adjr2, cp, bic, everything())%>%
  knitr::kable()
best(criterion_fw)%>% 
  select(p, rss, rsq, adjr2, cp, bic, everything())%>%
  knitr::kable()
best(criterion_sw_0.05)%>% 
  select(p, rss, rsq, adjr2, cp, bic, everything())%>%
  knitr::kable()
best(criterion_sw_0.10)%>% 
  select(p, rss, rsq, adjr2, cp, bic, everything())%>%
  knitr::kable()
best(criterion_fw_new)%>% 
  select(p, rss, rsq, adjr2, cp, bic, everything())%>%
  knitr::kable()

criterion_result <- full_join(best(criterion_bw), best(criterion_fw))%>%
  full_join(., best(criterion_sw_0.05))%>%
  full_join(., best(criterion_sw_0.10))%>%
  full_join(.,best(criterion_fw_new))%>%
  select(p, rss, rsq, adjr2, cp, bic, everything())


write_csv(criterion_result, "criterion_result.csv")

# ANOVA for nested model
anova(model_bw, model_sw_0.10)
anova(model_fw_new, model_sw_0.10)
anova(model_sw_0.05, model_sw_0.10)
anova(model_fw_new, model_sw_0.05)

model_base <- lm(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + temperature_cat + 
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure)
model_gender <- lm(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + temperature_cat + gender + 
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure)
model_marritalstat <- lm(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + temperature_cat + maritalstatus +
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure)
model_both <- lm(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + temperature_cat + gender + maritalstatus +
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure)
model_both_int <- lm(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + temperature_cat + gender + maritalstatus 
                    + gender * maritalstatus  + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure)
summary(model_both_int)
anova(model_base, model_gender)
anova(model_base, model_marritalstat)
anova(model_base, model_both)
anova(model_base, model_both_int)

par(mfrow = c(1, 2))
# Residuals vs fitted values plot
plot(fitted(model_sw_0.10), resid(model_sw_0.10), xlab = "Predicted/Fitted value", ylab = "Residual")
title("(a) Residual Plot for log_length_of_stay ")
abline(0, 0)

# Quantile - Quantile plot (QQ-plot)

qqnorm(resid(model_sw_0.10), xlab = "Expected Value", ylab = "Residual", main = "")
qqline(resid(model_sw_0.10))
title("(a) QQ Plot for log_length_of_stay")

plot(model_sw_0.10)

```

# backward selection for interaction

```{r}
interaction_full <-  lm(log_length_of_stay ~ is30dayreadmit + cindex 
                    + evisit + age + gender + maritalstatus + temperature_cat 
                    + insurancetype + heartrate_transformed 
                    + respirationrate_transformed 
                    + mean_arterial_pressure + age*temperature_cat 
                    + temperature_cat*heartrate_transformed
                    + is30dayreadmit*age 
                    + cindex*respirationrate_transformed  
                    + cindex*age
                    + mean_arterial_pressure*age, data= hos)
summary(interaction_full)

bwd_step1 = update(interaction_full, . ~ . -cindex:age)
summary(bwd_step1)

bwd_step2 = update(bwd_step1, . ~ . -cindex:respirationrate_transformed   )
summary(bwd_step2)

bwd_step3 = update(bwd_step2, . ~ . -temperature_cat:heartrate_transformed  )
summary(bwd_step3)

bwd_step4 = update(bwd_step3, . ~ . - age:temperature_cat )
summary(bwd_step4)

bwd_step5 = update(bwd_step4, . ~ . - is30dayreadmit:age  )
summary(bwd_step5)

#based on the results, none of the interaction term will be included in the model

```

#generating the statistics

```{r}
statistics <-  function(x) {
  average <- mean(x)
  median <- median(x)
  sd <- sd(x)
  quantile_1st <- quantile(x,probs = 0.25)
  quantile_3nd <- quantile(x,probs = 0.75)
  minimum <- min(x)
  maximum <- max(x)
  result <- data_frame(average,median,sd,quantile_1st,quantile_3nd , minimum,maximum)
  return(result)
}

hos%>%
  select(log_length_of_stay, evisit,  age, bmi, heartrate_transformed, respirationrate_transformed, mean_arterial_pressure ) %>%
  map(.,statistics)

hos_no_outlier%>%
  select(log_length_of_stay, evisit,  age, bmi, heartrate_transformed, respirationrate_transformed, mean_arterial_pressure )%>%
  map(.,statistics)

hos_no_outlier%>%
  select(log_length_of_stay, evisit,  age, bmi, heartrate_transformed, respirationrate_transformed, mean_arterial_pressure )%>%
  map(.,statistics)

hos%>%
  select(-log_length_of_stay, -evisit,  -age, -bmi, -heartrate_transformed, -respirationrate_transformed, -mean_arterial_pressure)%>%
  summary(.)

hos_no_outlier%>%
  select(-log_length_of_stay, -evisit,  -age, -bmi, -heartrate_transformed, -respirationrate_transformed, -mean_arterial_pressure)%>%
  summary(.)

hos_outlier%>%
  select(-log_length_of_stay, -evisit,  -age, -bmi, -heartrate_transformed, -respirationrate_transformed, -mean_arterial_pressure)%>%
  summary(.)

```

```{r}
setwise_subset2 = lm(log_length_of_stay ~ cindex + evisit + age + gender +  maritalstatus + insurancetype + bmi  + temperature_cat + heartrate_transformed + respirationrate_transformed + mean_arterial_pressure, data = hos_no_outlier)
summary(setwise_subset2)
summary(model_sw_0.10)
```

#Result interpretation

Initially, we get model (blablabla). Because this model violates the normalize assumption of the residual, we decided to remove outliers and refit another model. Compare the new model and the previous one, the new model loses the variable "is30dayreadmit" and have a new one "BMI". Overall, the adjusted R-squared increases by 15.5% and residual standard error decreased by 10.9%. For the covariates that stay in both models, the predictor "insurancetypeMedicare" became insignificant and the predictor "genderMale" became significant. And coefficients of the predictors changed, especially for predictor "temperature_catlow", which changed from -0.09679 to -0.05544. As for direction, all the predictors are consistent before and after.


# interpretaion about bootstrap












