---
title: "code_Xinyan"
author: "Xinyan Zheng"
date: "December 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(leaps)

#load the data
data_bwd = read.csv("./data/cleaned_data_for_analyses.csv") %>% 
  select(-X, -postalcode,-facilityname,-facilityzip, -patientid, -visitid, -date) %>% 
  mutate(is30dayreadmit = as.factor(is30dayreadmit), icu_flag = as.factor(icu_flag))
str(data_bwd)

```


```{r}
# using the selected variable from automatic method and go on using criterion-based method
attach(data_bwd)
model_bw <- lm(log_length_of_stay ~ is30dayreadmit + evisit + age 
                           + gender + maritalstatus + insurancetype
                           + heartrate_transformed + respirationrate_transformed 
                           + mean_arterial_pressure)
model_fw <- lm(log_length_of_stay ~ is30dayreadmit + evisit + age 
                           + race + insurancetype + heartrate_transformed 
                           + respirationrate_transformed + mean_arterial_pressure)

# for model yield from backward elimination method
criterion_bw <- regsubsets(log_length_of_stay ~ is30dayreadmit + evisit + age 
                           + gender + maritalstatus + insurancetype
                           + heartrate_transformed + respirationrate_transformed 
                           + mean_arterial_pressure, data=data_bwd, nvmax = 15)
res_bw <- summary(criterion_bw)
par(mfrow = c(2,2))
plot(1:10, res_bw$cp, xlab = "No of parameters", ylab = "Cp Statistic", main = " Cp Statisticof model from bw")
abline(0,1)
plot(1:10, res_bw$adjr2, xlab = "No of parameters", ylab = "Adj R2", main = " Adj R2 of model from bw" )
plot(1:10, res_bw$rss, xlab = "No of parameters", ylab = "rss", main = " rss of model from bw")
plot(1:10, res_bw$bic, xlab = "No of parameters", ylab = "bic",main = " bic of model from bw")

# for model yield from forward elimination method
criterion_fw <- regsubsets(log_length_of_stay ~ is30dayreadmit + evisit + age 
                           + race + insurancetype + heartrate_transformed 
                           + respirationrate_transformed + mean_arterial_pressure, data = data_bwd, nvmax = 15)
res_fw <- summary(criterion_fw)
par(mfrow = c(2,2))
plot(1:13, res_fw$cp, xlab = "No of parameters", ylab = "Cp Statistic", main = " Cp Statistic of model from fw")
abline(0,1)
plot(1:13, res_fw$adjr2, xlab = "No of parameters", ylab = "Adj R2", main = " Adj R2 of model from fw")
plot(1:13, res_fw$rss, xlab = "No of parameters", ylab = "rss", main = " rss of model from fw")
plot(1:13, res_fw$bic, xlab = "No of parameters", ylab = "bic", main = " bic of model from fw")
```

From plots, we see for model yield from backward elimination method, the best one would be 
log_length_of_stay = 
2.532 + 0.1708 \* is30dayreadmit +  0.06943 \* evisit + 0.009628 \* age 
+ 0.06741 \* genderMale + 0.07075 \* maritalstatusNot Married 
- 0.1648 \* insurancetypeMedicare - 0.2438 \* insurancetypePrivate 
- 0.002173 \* heartrate_transformed - 0.02048 \* respirationrate_transformed 
- 0.006086 \* mean_arterial_pressure.

On the other hand, for model yield from forward elimination method, the best one would be 

```{r, include=FALSE}
#using the function provided in class, using this way we can see the value for each criterion 
best <- function(model, ...) 
{
  subsets <- regsubsets(formula(model), model.frame(model), ..., nvmax = 15)
  subsets <- with(summary(subsets),
                  cbind(p = as.numeric(rownames(which)), which, rss, rsq, adjr2, cp, bic))
  
  return(subsets)
}  

# Select the 'best' 2 models of all subsets
res_bw <- round(best(model_bw, nbest = 1), 4)
res_fw <- round(best(model_fw, nbest = 1), 4)
```


```{r}
cri_bw <- c(res_bw[-1, 13:17], AIC(model_bw))
cri_fw <- c(res_fw[,16:20], AIC(model_fw))
rbind(cri_bw,cri_fw)
```
