---
title: "Backward Elimination"
author: "Shan-Shan Song, ss5422@columbia.edu"
date: "12/10/2017"
output: html_document
---

```{r bwd_import, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(broom)
library(plyr)
data_bwd = read.csv("./data/cleaned_data_for_analyses.csv") %>% 
  select(-X, -postalcode,-facilityname,-facilityzip, -patientid, -visitid, -date) %>% 
  mutate(is30dayreadmit = as.factor(is30dayreadmit), icu_flag = as.factor(icu_flag))
str(data_bwd)
```

- start with all predictors in the model

```{r bwd_full, message=FALSE, warning=FALSE, include=FALSE}
# fit
bwd_fit_full = lm(log_length_of_stay ~ ., data = data_bwd)
arrange(tidy(bwd_fit_full), desc(p.value))
```

- remove the predictor with highest p-value
- refit the model and move on
- stop when all p-values <= **alpha_crit (p-to-remove) = 0.05**.

```{r bwd_back, message=FALSE, warning=FALSE, include=FALSE}
# step 1: no race
bwd_step1 = update(bwd_fit_full, . ~ . -race)
arrange(tidy(bwd_step1), desc(p.value))
step1_pvalue = tidy(bwd_step1) %>% select(term, p.value)

# step 2: no cindex
bwd_step2 = update(bwd_step1, . ~ . -cindex)
arrange(tidy(bwd_step2), desc(p.value))
step2_pvalue = tidy(bwd_step2) %>% select(term, p.value)

# step 3: no mews
bwd_step3 = update(bwd_step2, . ~ . -mews)
arrange(tidy(bwd_step3), desc(p.value))
step3_pvalue = tidy(bwd_step3) %>% select(term, p.value)

# step 4: no religion
bwd_step4 = update(bwd_step3, . ~ . -religion)
arrange(tidy(bwd_step4), desc(p.value))
step4_pvalue = tidy(bwd_step4) %>% select(term, p.value)

# step 5: no o2sat_cat
bwd_step5 = update(bwd_step4, . ~ . -o2sat_cat)
arrange(tidy(bwd_step5), desc(p.value))
step5_pvalue = tidy(bwd_step5) %>% select(term, p.value)

# step 6: no icu_flag
bwd_step6 = update(bwd_step5, . ~ . -icu_flag)
arrange(tidy(bwd_step6), desc(p.value))
step6_pvalue = tidy(bwd_step6) %>% select(term, p.value)

# step 7: no temperature_cat
bwd_step7 = update(bwd_step6, . ~ . -temperature_cat)
arrange(tidy(bwd_step7), desc(p.value))
step7_pvalue = tidy(bwd_step7) %>% select(term, p.value)

# step 8: no bmi
bwd_step8 = update(bwd_step7, . ~ . -bmi)
arrange(tidy(bwd_step8), desc(p.value))
step8_pvalue = tidy(bwd_step8) %>% select(term, p.value)

# combine pvalues each step into a table
for (i in 1:8){
  if (i == 1){
    step_pvalue = step1_pvalue %>% rename(c("p.value" = "pvalue_step1"))
    next}
  loop_name = paste0("step",i,"_pvalue",sep = "")
  step_pvalue = merge(step_pvalue, eval(parse(text = loop_name)), all = TRUE, by = "term") %>% 
    rename(c("p.value" = paste0("pvalue_step",i)))
}
```

```{r bwd_results}
# backward p-values
step_pvalue %>% DT::datatable()
# summary of model from backward elimination
bwd_step8 %>% summary()
```